\subsection{Part III: Determination of  the Standard error }

The Standard error was calculated using the following function
\lstinputlisting[language=R, firstline=52, lastline=55]{../Q2_ii_iii.R}


\begin{table}[h!]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Category           & Standard Error \\
        \midrule
        Small Narrowbodies & 57.20074       \\
        Large Narrowbodies & 55.25397       \\
        Widebodies         & 77.62307       \\
        Total Fleet        & 58.85758       \\
        \bottomrule
    \end{tabular}
    \caption{Standard Error values for different aircraft categories}
    \label{tab:rsquared_se}
\end{table}

The Standard Error (SE) is a measure of the accuracy of predictions made by the model, indicating the average distance that the observed values fall from the regression line. A lower SE suggests that the model’s predictions are closer to the actual values, while a higher SE implies greater dispersion of observed values from the predicted values.

\begin{itemize}
    \item \textbf{Small Narrowbodies:} The Standard Error is 57.20074, meaning that the observed values for small narrowbody aircraft, on average, deviate from the predicted values by approximately 57.20 units. This indicates a relatively moderate level of dispersion.

    \item \textbf{Large Narrowbodies:} With a Standard Error of 55.25397, the large narrowbody aircraft category shows slightly less dispersion compared to small narrowbodies, implying that predictions are somewhat more accurate for this category.

    \item \textbf{Widebodies:} The Standard Error for widebody aircraft is 77.62307, indicating a higher level of dispersion in predictions compared to the narrowbody categories. This suggests that the model's accuracy is lower for widebodies, with actual values often deviating more from the predictions.

    \item \textbf{Total Fleet:} For the total fleet, the Standard Error is 58.85758, reflecting the overall deviation across all categories. This value is similar to that of the small narrowbodies, indicating a moderate level of dispersion for the entire fleet.

\end{itemize}